\documentclass[10pt, oneside]{article}
\usepackage[hmargin={1in, 1in}, vmargin={0.7in, 1in}]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{setspace}
\setlength{\parindent}{0pt}
\titlespacing{\subsection}{0pt}{10pt}{-5pt}
\hypersetup{
  colorlinks = true, %Colours links instead of ugly boxes
  urlcolor = black %Colour for external hyperlinks
} 
% \usepackage{xeCJK}
% \setCJKmainfont{Songti SC}
	
\title{\vspace{-5em}}
\date{}

\begin{document}
\maketitle

\section*{Jing Zeng}
\vspace{10pt}

\subsection*{Contact}
\noindent\rule{\textwidth}{1pt}
Department of Statistics, Florida State University\\
117 N. Woodward Ave., P.O. Box 3064330\\
Tallahassee, FL 32306-4330, USA\\
Email: jz17c@my.fsu.edu
% Github: \url{https://github.com/leozeng15}\\
% Website: \url{https://jzeng.site/}

\subsection*{Education}
\noindent\rule{\textwidth}{1pt}
\textbf{Florida State University}, Department of Statistics\\
Ph.D. in Statistics \hfill 08/2017 - 05/2022\\
Co-advisors: Dr. Xin Zhang and Dr. Qing Mai\\[-2mm]

\textbf{University of Science and Technology of China}, School of Mathematical Sciences\\
B.S. in Mathematics and Applied Mathematics \hfill 09/2013 - 06/2017\\
% Advisor: Dr. Min Yuan

\subsection*{Research Interests}
\noindent\rule{\textwidth}{1pt}
\vspace{-6mm}
\begin{itemize}[itemsep=-1pt]
    \item Applications in medical science.
    \item Dimension reduction.
    \item High-dimensional statistics.
    \item Machine learning.
    \item Robust statistics.
    \item Tensor data analysis.
\end{itemize}

\subsection*{Publications}
\noindent\rule{\textwidth}{1pt}\\[1mm]
``$\dagger$'' indicates alphabetical authorship.
\begin{enumerate}[itemsep=0pt]
    \item Zeng, J., Mai, Q. and Zhang, X. (2021+). Subspace Estimation with Automatic Dimension and Variable Selection in Sufficient Dimension Reduction. \textit{Journal of the American Statistical Association}. Under revision (invited major revision).
    \item $\dagger$ Li, L., Zeng, J. and Zhang, X. (2021+). Generalized Liquid Association Analysis for Multimodal Data Integration. \textit{Journal of the American Statistical Association}. Revision submitted (invited major revision). arXiv preprint: https://arxiv.org/abs/2008.03733.
    \item Zeng, J., Zhang, X. and Mai, Q. (2021). An Efficient Convex Formulation for Reduced-Rank Linear Discriminant Analysis in High Dimensions. \textit{Statistica Sinica}, accepted.
    \item Zeng, J., Wang, W. and Zhang, X. (2021). TRES: An R Package for Tensor Regression and Envelope Algorithms. \textit{Journal of Statistical Software}, 99, 1-31.
\end{enumerate}

\subsection*{Honors and Awards}
\noindent\rule{\textwidth}{1pt}
\begin{itemize}[itemsep=-1pt]
    \item Outstanding Teaching Assistant Award (OTAA) nomination, Florida State University. \hfill 01/2020
    % \begin{itemize}[topsep=-2pt,itemsep=-1pt]

    \vspace{-0.5mm}
    \textit{(Only two teaching assistants were nominated from each department.)}
    % \end{itemize}
    \item Best First Year Student in Applied Statistics Award (top 10), Florida State University. \hfill 10/2018
    % \begin{itemize}[topsep=-2pt,itemsep=-1pt]

    \vspace{-0.5mm}
    \textit{(The award was presented in recognition of outstanding achievement as a graduate student.)}
    \item Scholarship for Outstanding Students, Third Prize (top 20\%), University of Science and Technology of China. \hfill 09/2015
    \item Scholarship for Outstanding Students, Second Prize (top 10\%), University of Science and Technology of China. \hfill 09/2014
\end{itemize}

\subsection*{Software}
\noindent\rule{\textwidth}{1pt}
\begin{enumerate}[itemsep=0pt]
    \item R package: \textbf{TRES} (\url{https://cran.r-project.org/web/packages/TRES/index.html}).
\end{enumerate}

\subsection*{Teaching}
\noindent\rule{\textwidth}{1pt}
\vspace{-6mm}
\begin{itemize}[itemsep=-1pt]
    \item Solo Instructor, Florida State University
    \begin{itemize}[topsep=-2pt,itemsep=-1pt]
        \item STA 2122: Introduction to Applied Statistics (Summer 2018, Fall 2018, Spring 2019)
    \end{itemize}
    \item Teaching Assistant, Florida State University
    \begin{itemize}[topsep=-2pt,itemsep=-1pt]
        \item STA 5934-0001: Tensor Data Analysis (Spring 2020)
        \item STA 5934-0002: Deep Learning (Spring 2020)
        \item STA 5934-0004: Statistical Computing with Python (Spring 2020)
        \item STA 2122: Introduction to Applied Statistics (Fall 2017, Spring 2018)
    \end{itemize}
    \item Teaching Assistant, University of Science and Technology of China
    \begin{itemize}[topsep=-2pt,itemsep=-1pt]
        \item Probability and Mathematical Statistics (Fall 2016).
    \end{itemize}
\end{itemize}

\subsection*{Other Academic Experience}
\noindent\rule{\textwidth}{1pt}
\begin{itemize}[itemsep=-1pt]
    \item Research Assistant (under supervision of Dr. Xin Zhang and Dr. Qing Mai). \\
    Florida State University \hfill 06/2019 - Present
    \item Referee: \textit{WIREs Computational Statistics}, \textit{Biometrics}.
    \item Presenter: Invited talk at International Conference on Econometrics and Statistics (EcoSta).\\
    Hong Kong, China (Virtual) \hfill 06/2021
    \item Presenter: Contributed talk at Joint Statistical Meetings (JSM).\\
    Denver, CO \hfill 07/2019

    % \item Seminar organizer, Florida State University \\
    % Tallahassee, FL \hfill Aug 2019 - Dec 2019
    % \begin{itemize}[topsep=-2pt,itemsep=-1pt]
    %     \item Organized the department seminar with topic: \textit{High-dimensional data and dimension reduction}.
    %     \item Gave several presentations with topics on the personal research and some self-studied skills.
    % \end{itemize}

\end{itemize}


% \subsection*{References}
% \noindent\rule{\textwidth}{1pt}
% \begin{itemize}[itemsep=0pt]
%     \item Xin Zhang, Associate Professor \\
%     Department of Statistics, Florida State University\\
%     214 OSB, 117 N. Woodward Ave., Tallahassee, FL 32306-4330, USA\\
%     Email: henry@stat.fsu.edu
%     \item Qing Mai, Associate Professor \\
%     Department of Statistics, Florida State University\\
%     214 OSB, 117 N. Woodward Ave., Tallahassee, FL 32306-4330, USA\\
%     Email: qmai@fsu.edu
%     \item Lexin Li, Professor\\
%     Department of Biostatistics and Epidemiology, University of California, Berkeley\\
%     2121 Berkeley Way, Berkeley, CA 94720-7360, USA\\
%     Email: lexinli@berkeley.edu
% \end{itemize}


\end{document}