\documentclass[10pt, oneside]{article}
\usepackage[hmargin={1in, 1in}, vmargin={0.7in, 1in}]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{setspace}
\setlength{\parindent}{0pt}
\titlespacing{\subsection}{0pt}{10pt}{-5pt}
\hypersetup{
  colorlinks = true, %Colours links instead of ugly boxes
  urlcolor = black %Colour for external hyperlinks
} 
\usepackage{xeCJK}
\setCJKmainfont{Songti SC}
	
\title{\vspace{-5em}}
\date{}

\begin{document}
\maketitle

\section*{曾靖}
\vspace{10pt}

\subsection*{联系方式}
\noindent\rule{\textwidth}{1pt}
Department of Statistics, Florida State University\\
117 N. Woodward Ave., P.O. Box 3064330\\
Tallahassee, FL 32306-4330, USA\\
Email: jz17c@my.fsu.edu
% Github: \url{https://github.com/leozeng15}\\
% Website: \url{https://jzeng.site/}

\subsection*{教育经历}
\noindent\rule{\textwidth}{1pt}
\textbf{佛罗里达州立大学 (Florida State University)}, 统计系 (Department of Statistics)\\
统计学在读博士 (GPA: 4.0/4.0) \hfill 08/2017 - 05/2022\\
导师: Dr. Xin Zhang and Dr. Qing Mai\\[-2mm]

\textbf{中国科学技术大学}, 数学科学学院\\
数学与应用数学专业理学学士 (GPA: 3.72/4.3) \hfill 09/2013 - 06/2017
% Advisor: Min Yuan

\subsection*{研究方向}
\noindent\rule{\textwidth}{1pt}
\vspace{-6mm}
\begin{itemize}[itemsep=-1pt]
    \item 统计在医学上的应用 (Applications in medical science)
    \item 数据降维 (Dimension reduction)
    \item 高维统计 (High-dimensional statistics)
    \item 机器学习 (Machine learning)
    \item 稳健统计 (Robust statistics)
    \item 张量数据分析 (Tensor data analysis)
\end{itemize}

\subsection*{论文发表情况}
\noindent\rule{\textwidth}{1pt}
\begin{enumerate}[itemsep=0pt]
    \item Zeng, J., Mai, Q. and Zhang, X. (2021+). Subspace Estimation with Automatic Dimension and Variable Selection in Sufficient Dimension Reduction. \textit{Journal of the American Statistical Association}. Under revision (invited major revision).
    \item Li, L., Zeng, J. and Zhang, X. (2021+). Generalized Liquid Association Analysis for Multimodal Data Integration. (Alphabetical ordered) \textit{Journal of the American Statistical Association}. Revision submitted (invited major revision). arXiv preprint: https://arxiv.org/abs/2008.03733.
    \item Zeng, J., Zhang, X. and Mai, Q. (2021). An Efficient Convex Formulation for Reduced-Rank Linear Discriminant Analysis in High Dimensions. \textit{Statistica Sinica}, accepted.
    \item Zeng, J., Wang, W. and Zhang, X. (2021). TRES: An R Package for Tensor Regression and Envelope Algorithms. \textit{Journal of Statistical Software}, 99, 1-31.
\end{enumerate}

\subsection*{荣誉与获奖情况}
\noindent\rule{\textwidth}{1pt}
\begin{itemize}[itemsep=-1pt]
    \item Outstanding Teaching Assistant Award (OTAA) nomination, 佛罗里达州立大学. \hfill 01/2020
    % \begin{itemize}[topsep=-2pt,itemsep=-1pt]

    \vspace{-0.5mm}
    \textit{(Only two teaching assistants were nominated from each department.)}
    % \end{itemize}
    \item Best First Year Student in Applied Statistics Award (top 10), 佛罗里达州立大学. \hfill 10/2018
    % \begin{itemize}[topsep=-2pt,itemsep=-1pt]

    \vspace{-0.5mm}
    \textit{(The award was presented in recognition of outstanding achievement as a graduate student.)}
    \item 优秀学生奖学金, 铜奖 (top 20\%), 中国科学技术大学. \hfill 09/2015
    \item 优秀学生奖学金, 银奖 (top 10\%), 中国科学技术大学. \hfill 09/2014
\end{itemize}

\subsection*{统计软件}
\noindent\rule{\textwidth}{1pt}
\begin{enumerate}[itemsep=0pt]
    \item R package: \textbf{TRES} (\url{https://cran.r-project.org/web/packages/TRES/index.html}).
\end{enumerate}

\subsection*{教学经历}
\noindent\rule{\textwidth}{1pt}
\vspace{-6mm}
\begin{itemize}[itemsep=-1pt]
    \item 讲师 (Solo Instructor), 佛罗里达州立大学
    \begin{itemize}[topsep=-2pt,itemsep=-1pt]
        \item STA 2122: 应用统计初步 (Introduction to Applied Statistics) (Summer 2018, Fall 2018, Spring 2019)
    \end{itemize}
    \item 助教 (Teaching Assistant), 佛罗里达州立大学
    \begin{itemize}[topsep=-2pt,itemsep=-1pt]
        \item STA 5934-0001: 张量数据分析 (Tensor Data Analysis) (Spring 2020)
        \item STA 5934-0002: 深度学习 (Deep Learning) (Spring 2020)
        \item STA 5934-0004: Python统计计算 (Statistical Computing with Python) (Spring 2020)
        \item STA 2122: 应用统计初步 (Introduction to Applied Statistics) (Fall 2017, Spring 2018)
    \end{itemize}
    \item 助教,中国科学技术大学 
    \begin{itemize}[topsep=-2pt,itemsep=-1pt]
        \item 概率论与数理统计 (2016秋季学期).
    \end{itemize}
\end{itemize}

\subsection*{其他学术经历}
\noindent\rule{\textwidth}{1pt}
\begin{itemize}[itemsep=-1pt]
    \item 研究助理 (Research Assistant) (under supervision of Dr. Xin Zhang and Dr. Qing Mai). \\
    佛罗里达州立大学 \hfill 06/2019 - Present
    \item 审稿评委: \textit{WIREs Computational Statistics}, \textit{Biometrics}.
    \item 会议报告: Invited talk at International Conference on Econometrics and Statistics (EcoSta).\\
    中国，香港 (网络会议) \hfill 06/2021
    \item 会议报告: Contributed talk at Joint Statistical Meetings (JSM).\\
    美国科罗拉多州，丹佛 \hfill 07/2019

    % \item Seminar organizer, Florida State University \\
    % Tallahassee, FL \hfill Aug 2019 - Dec 2019
    % \begin{itemize}[topsep=-2pt,itemsep=-1pt]
    %     \item Organized the department seminar with topic: \textit{High-dimensional data and dimension reduction}.
    %     \item Gave several presentations with topics on the personal research and some self-studied skills.
    % \end{itemize}

\end{itemize}


\subsection*{推荐人信息}
\noindent\rule{\textwidth}{1pt}
\begin{itemize}[itemsep=0pt]
    \item Xin Zhang, Associate Professor \\
    Department of Statistics, Florida State University\\
    214 OSB, 117 N. Woodward Ave., Tallahassee, FL 32306-4330, USA\\
    Email: henry@stat.fsu.edu
    \item Qing Mai, Associate Professor \\
    Department of Statistics, Florida State University\\
    214 OSB, 117 N. Woodward Ave., Tallahassee, FL 32306-4330, USA\\
    Email: qmai@fsu.edu
    \item Lexin Li, Professor\\
    Department of Biostatistics and Epidemiology, University of California, Berkeley\\
    2121 Berkeley Way, Berkeley, CA 94720-7360, USA\\
    Email: lexinli@berkeley.edu
\end{itemize}


\end{document}