\documentclass[10pt, oneside]{article}
\usepackage[hmargin={1in, 1in}, vmargin={0.7in, 1in}]{geometry}
% \usepackage{Mylatex}
\RequirePackage{hyperref}
\RequirePackage{amsmath,amsthm,amsfonts}
\RequirePackage{bm}
\RequirePackage{enumitem}
\RequirePackage{multirow}
\RequirePackage{multicol}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{setspace}
\setlength{\parindent}{0pt}
\titlespacing{\subsection}{0pt}{10pt}{-5pt}
\hypersetup{
  colorlinks = true, %Colours links instead of ugly boxes
  urlcolor = black %Colour for external hyperlinks
} 

	
\title{\vspace{-5em}}
\date{}

\begin{document}
\maketitle

\section*{Jing Zeng}
\vspace{10pt}

\subsection*{Contact}
\noindent\rule{\textwidth}{1pt}
Department of Statistics, Florida State University\\
214 OSB, 117 N. Woodward Ave., P.O. Box 3064330\\
Tallahassee, FL 32306-4330, USA\\
Email: \href{mailto:jz17c@my.fsu.edu}{jz17c@my.fsu.edu}\\
Github: \url{https://github.com/leozeng15}\\
Website: \url{https://ani.stat.fsu.edu/~jing.zeng/}

\subsection*{Education}
\noindent\rule{\textwidth}{1pt}
\textbf{Florida State University}, Department of Statistics\\
Ph.D. in Statistics (GPA: 4.0/4.0) \hfill Aug 2017 - May 2022\\
Advisor: Xin Zhang\\[-10pt]

\textbf{University of Science and Technology of China}, School of Mathematical Sciences\\
B.S. in Probability and Statistics (GPA: 3.72/4.3) \hfill Sep 2013 - June 2017

\subsection*{Skills}
\noindent\rule{\textwidth}{1pt}
\textbf{Languages}: R (5+ years), Python, MATLAB, C, LaTeX, SQL\\[-10pt]

\textbf{Utilities}: Git, Linux, HPC, R package writing, Jupyter Notebook, Python scientific packages.

\subsection*{Publications}
\noindent\rule{\textwidth}{1pt}
\begin{enumerate}[itemsep=0pt]
    \item 
    Li, L., Zeng, J. and Zhang, X. (2021). Generalized Liquid Association Analysis for Multimodal Data Integration. (Alphabetical order of authors.) \textit{Journal of the American Statistical Association}, under revision. arXiv preprint: https://arxiv.org/abs/2008.03733.

    \item Zeng, J., Mai, Q. and Zhang, X. (2021). Subspace Estimation with Automatic Dimension and Variable Selection in Sufficient Dimension Reduction. \textit{Journal of the American Statistical Association}, under revision.
    
    \item Zeng, J., Zhang, X. and Mai, Q. (2021). An Efficient Convex Formulation for Reduced-Rank Linear Discriminant Analysis in High Dimensions. \textit{Statistica Sinica}, under revision.
    
    \item Zeng, J., Wang, W. and Zhang, X. (2020+). TRES: An R Package for Tensor Regression and Envelope Algorithms. \textit{Journal of Statistical Software}, accepted. 
\end{enumerate}

\subsection*{Projects}
\noindent\rule{\textwidth}{1pt}
\begin{enumerate}[itemsep=0pt]
    \item A New Minimax-optimal Approach to Sliced Inverse Regression in High Dimensions\\
    \textit{Joint work with Keqian Min, Prof. Qing Mai and Prof. Xin Zhang} \hfill Sep 2020 - Present
    \begin{itemize}[topsep=-2pt,itemsep=-1pt]
        \item Conducted numerical studies and participate in discussion.
    \end{itemize}
    \item An Efficient Convex Formulation for Reduced-Rank Linear Discriminant Analysis in High Dimensions.\\
    \textit{Joint work with Prof. Xin Zhang and Prof. Qing Mai} \hfill July 2020 - Present
    \begin{itemize}[topsep=-2pt,itemsep=-1pt]
        \item Established a model-based interpretation of the reduced-rank LDA, and developed a convex formulation for parameter estimation in high-dimensional setting.
        \item Conducted exhaustive numerical studies and took charge of the theoretical proofs.
        \item Wrote and submitted the paper as the first author.
    \end{itemize}
    \item Generalized Liquid Association Analysis for Multimodal Data Integration \\
    \textit{Joint work with Prof. Lexin Li and Prof. Xin Zhang} \hfill Feb 2020 - Present
    \begin{itemize}[topsep=-2pt,itemsep=-1pt]
        \item Proposed a non-trivial sparse and low-rank tensor decomposition algorithm.
        \item Conducted exhaustive simulation study, analysed a neural imaging data set using our proposal, and took charge of the theoretical proofs.
        \item Wrote and submitted the paper as a contribution-equivalent author.
    \end{itemize}

    \item R package writing: \textbf{TRES} (available at \url{https://CRAN.R-project.org/package=TRES})\\
    \textit{Joint work with Dr. Wenjing Wang and Prof. Xin Zhang} \hfill June 2019 - Dec 2020
    \begin{itemize}[topsep=-2pt,itemsep=-1pt]
        \item Wrote a set of S3 methods with easy-to-use interfaces.
        \item Systematically improved the package by rewriting the functions in a more user-friendly manner and providing more detailed and informative help documentations.
        \item The paper is accepted by \textit{Journal of Statistical Software}.
    \end{itemize}

    \item Subspace Estimation with Automatic Dimension and Variable Selection (SEAS)\\
    \textit{Joint work with Prof. Qing Mai and Prof. Xin Zhang} \hfill  Jan 2018 - Present

    \begin{itemize}[topsep=-2pt,itemsep=-1pt]
        \item Proposed an efficient ADMM algorithm, conducted the exhaustive numerical studies, and is responsible for most part of the theoretical proofs.
        \item Wrote and submitted the paper as the first author.
    \end{itemize}

\end{enumerate}

\subsection*{Professional Experience}
\noindent\rule{\textwidth}{1pt}
\begin{itemize}[itemsep=-1pt]
    \item Referee: \textit{WIREs Computational Statistics}, \textit{Biometrics}.
    \item Presenter, invited talk at International Conference on Econometrics and Statistics (EcoSta)\\
    Hong Kong, China (Virtual) \hfill June 2021
    \item Presenter, contributed talk at Joint Statistical Meetings (JSM)\\
    Denver, CO \hfill July 2019

    \item Seminar organizer, Florida State University \\
    Tallahassee, FL \hfill Aug 2019 - Dec 2019
    \begin{itemize}[topsep=-2pt,itemsep=-1pt]
        \item Organized the seminar with the topic: \textit{High-dimensional data and dimension reduction}.
        \item Gave several presentations with topics on the personal research and some self-studied skills.
    \end{itemize}

    \item Research assistant, Florida State University\\
    Tallahassee, FL \hfill June 2019 - Present
    \begin{itemize}[topsep=-2pt,itemsep=-1pt]
        \item Conducted four projects with Prof. Xin Zhang and helped organize the seminar successfully.
        \item Published the R package \textbf{TRES} on \href{https://CRAN.R-project.org/package=TRES}{CRAN}.
        \item One paper has been accepted by \textit{Journal of Statistical Software}, and three papers have been submitted to top peer-reviewed journals.
    \end{itemize}

    \item Solo instructor \& Teaching assistant, Florida State University\\
    Tallahassee, FL \hfill Aug 2017 - May 2019
    \begin{itemize}[topsep=-2pt,itemsep=-1pt]
        \item Independently taught two sections with four classes a week, 50 mins per class.
        \item Organized the group activity in class and successfully activated the students.
        \item Received around 5/5 median evaluation score.
    \end{itemize}

    \item Summer intern, Industrial and Commercial Bank of China\\
    Hefei, P. R. China \hfill Jul 2016 - Aug 2016
    \begin{itemize}[topsep=-2pt,itemsep=-1pt]
        \item Studied the application of system maintenance in bank system.
        \item Used SQL (with softwares MySQL and Oracle) to manipulate database.
    \end{itemize}
\end{itemize}

\subsection*{Achievements}
\noindent\rule{\textwidth}{1pt}
\begin{itemize}[itemsep=-1pt]
    \item Outstanding Teaching Assistant Award (OTAA) nomination, Florida State University, Jan 2020
    \begin{itemize}[topsep=-2pt,itemsep=-1pt]
        \item Only one teaching assistant was nominated from each department.
    \end{itemize}
    \item Best First Year Student in Applied Statistics Award (top 10), Florida State University, Oct 2018
    \begin{itemize}[topsep=-2pt,itemsep=-1pt]
        \item The award was presented in recognition of outstanding achievement as a graduate student.
    \end{itemize}
    \item Scholarship for Outstanding Students, First Prize (top 5\%), University of Science and Technology of China, Sep 2016
    \item Scholarship for Outstanding Students, Third Prize (top 20\%), University of Science and Technology of China, Sep 2015
    \item Scholarship for Outstanding Students, Second Prize (top 10\%), University of Science and Technology of China, Sep 2014
\end{itemize}

\subsection*{Relevant Courses}
\noindent\rule{\textwidth}{1pt}
\begin{itemize}[itemsep=-1pt]
    \item \textbf{Online}: Advanced Machine Learning, Neural Networks and Deep Learning, Intro to SQL for Data Science.\\[-10pt]
    \item \textbf{Classroom}: Computational Methods in Statistics, Advanced Probability and Inference, Application in Statistics (Linear Regression and Generalized Linear Model), Time Series Analysis, Stochastic Process, Non-parametric Statistics, Real Analysis, Complex Analysis, Functional Analysis, Differential Equation, Computer Programming (C and C++), Data Structure and Database.
\end{itemize}

\end{document}